A \proglang{Python}/\proglang{Zig} optimized and customizable implementation for the $\rho_{DCCA}$ and $DMC_x^2$ methods

### 2025-02-27 paper_v02/article.tex
paper version 02

The code above calculates the slope and the intercept of a linear least squares fit. The function runs on every box for every time scale.In the optimized version, for consecutive boxes, the value of the sums from the previous box is used to calculate the next one without a loop for every item in the box.

@@

The expression in Eq.~\ref{eq:sum_opt_y} stands that the sum of the values in a box is equal to the sum of the previous box minus the first value of the previous box plus the last value of the current box. According to that, the 
when a box is calculated, the sum and the first value is saved in temporary variables, to calculate the next sum, the previous sum is subtracted from the temporary variable and the new value is added. The bigger the box, the bigger the gain in performance.

>>>>

The code above calculates the slope and the intercept of a linear least squares fit. The function runs on every box for every time scale. In the optimized version, for consecutive boxes, the value of the sums from the previous box is used to calculate the next one without a loop for every item in the box. This technic proved to be very efficient in increasing performance. the expressions below show the effectiveness of the optimized algorithm.

@@

The expression in Eq.~\ref{eq:sum_opt_y} states that the sum of the values in a box is equal to the sum of the previous box minus the first value of the previous box plus the last value of the current box. According to that, when a box is calculated, the sum and the first value are saved in temporary variables. To calculate the next sum, the previous sum is subtracted from the temporary variable and the new value is added. The larger the box, the greater the performance gain.
